Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-07-06 kappa.tex
Rescale all intro photos to 500x300 px.
Add Susitna glacier photo by Austin Post.

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-glacier-crevasses}
    \hspace{1cm}
    \subgraphics{b}{photo-glacier-fold}
  }
  \caption{Different mechanical behaviours of glacier ice.
           \textbf{(a)} Brittle behaviour. Ice flowing over a hidden bedrock
           knob, resulting in fracturing at the glacier surface.
           Glacier Blanc, French Alps.
           \textbf{(b)} Ductile behaviour. Mountain glacier calving into a
           small lake, revealing a folded structure formed by deformed rock
           layers in the ice.}
  \label{fig:glacier-mechanics}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics[width=50mm]{a}{photo-glacial-valley}
    \hspace{1cm}
    \subgraphics[width=50mm]{b}{photo-erratic-boulder}
    \hspace{1cm}
    \subgraphics[width=50mm]{c}{photo-melt-channels}
  }
  \caption{Different indicators of past glaciation.
           \textbf{(a)} Glacial valley, exhibiting a broad, U-shaped profile
           characteristic of erosion by glaciers.
           Cirque du Fer-\`{a}-Cheval, French Alps.
           \textbf{(b)} Erratic boulders, deposited in an improbable
           arrangement as the glacier melted underneath.
           Finse area, Norwegian Scandes.
           \textbf{(c)} Lateral meltwater channels, formed on a gentle slope
           as the ice margin retreated towards the valley bottom. Tuya Lake
           area, Canadian Cordillera.}
  \label{fig:glaciation-indicators}
\end{figure}

>>>>

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-glacier-crevasses}
    \hspace{1cm}
    \subgraphics{b}{photo-glacier-susitna}
    \hspace{1cm}
    \subgraphics{c}{photo-glacier-fold}
  }
  \caption{Illustration of various glacier ice behaviours.
           \textbf{(a)} Surface crevasses formed by ice flow over a hidden
           bedrock knob. Glacier Blanc, French Alps, 2004.
           \textbf{(b)} Medial moraines illustrating downhill ice flow on
           Susitna Glacier, Alaska Range, by Austin Post, 1970
           \citep{NSIDC.2009}.
           \textbf{(c)} Mountain glacier calving into a small lake, revealing a
           folded structure formed by deformed debris layers in the ice.
           Glacier d'Arsine, French Alps, 2004.}
  \label{fig:glacier-mechanics}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-glacial-valley}
    \hspace{1cm}
    \subgraphics{b}{photo-erratic-boulder}
    \hspace{1cm}
    \subgraphics{c}{photo-melt-channels}
  }
  \caption{Different indicators of past glaciation.
           \textbf{(a)} Glacial valley, exhibiting a broad, U-shaped profile
           characteristic of erosion by glaciers.
           Cirque du Fer-\`{a}-Cheval, French Alps, 2013.
           \textbf{(b)} Erratic boulders, deposited in an improbable
           arrangement as the glacier melted underneath.
           Finse area, Norwegian Scandes, 2011.
           \textbf{(c)} Lateral meltwater channels, formed on a gentle slope
           as the ice margin retreated towards the valley bottom. Tuya Lake
           area, Canadian Cordillera, 2012.}
  \label{fig:glaciation-indicators}
\end{figure}
